Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2013-02-20 omrp.tex
Spaced omrp.tex so that each line corresponds to a sentence.  This way, Git will automatically keep track of how sentences change in the paper
Updated Guzin's contact information

% AUTHOR: Enter the authors of the article, see end of the example document for further examples
\author{David~Love$^{a}$\ \ and G\"{u}zin~Bayraksan$^{b}$\thanks{Corresponding author. Tel.: +1 520-621-2605. Fax:+1 520-621-6555}\\[6pt]
{\small
      $^{a}$ Program in Applied Mathematics, University of Arizona, Tucson, AZ 85721, USA, \texttt{dlove@math.arizona.edu}} \\
{\small 
      $^{b}$ Systems and Industrial Engineering, University of Arizona, Tucson, AZ 85721, USA, \texttt{guzinb@sie.arizona.edu}}}

@@

We empirically tested the effectiveness of OMRP on three problems. The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$, the second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations, and the final is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables.  A description of CEP1 can be found in \cite{higle1996}, and a description of 10D is available in \cite{kleywegt2002sample}. . The instance of the newsvendor problem as well as the candidate solutions used for both problems can be found in \cite{Bayraksan2006}, except here we used a discrete uniform demand distribution for the newsvendor problem.  Both CEP1 and newsvendor can be written as two-stage stochastic linear programs with recourse. CEP1 was solved with the regularized decomposition algorithm of \cite{ruszczynski1986regularized}, using the accelerated version 
of the 
algorithm implemented in C++ \cite{ruszczynski1997accelerating}. The newsvendor problem was solved using the quicksort algorithm in C++, and 10D was solved using dynamic programming.  In all three cases, we used the Mersenne Twister algorithm to generate random samples \cite{wagner_twister_09}.

>>>>

% AUTHOR: Enter the authors of the article, see end of the example document for further examples
\author{David~Love$^{a}$\ \ and G\"{u}zin~Bayraksan$^{b}$\thanks{Corresponding author. Tel.: +1 520-621-2605. Fax:+1 614-292-7852}\\[6pt]
{\small
      $^{a}$ Program in Applied Mathematics, University of Arizona, Tucson, AZ 85721, USA, \texttt{dlove@math.arizona.edu}} \\
{\small 
      $^{b}$ Integrated Systems Engineering, The Ohio State University, Columbus, OH 43210, USA, \texttt{bayraksan.1@osu.edu}}}

@@

We empirically tested the effectiveness of OMRP on three problems. 
The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$, the second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations, and the final is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables.  
A description of CEP1 can be found in \cite{higle1996}, and a description of 10D is available in \cite{kleywegt2002sample}. 
The instance of the newsvendor problem as well as the candidate solutions used for both problems can be found in \cite{Bayraksan2006}, except here we used a discrete uniform demand distribution for the newsvendor problem.  
Both CEP1 and newsvendor can be written as two-stage stochastic linear programs with recourse. 
CEP1 was solved with the regularized decomposition algorithm of \cite{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \cite{ruszczynski1997accelerating}. 
The newsvendor problem was solved using the quicksort algorithm in C++, and 10D was solved using dynamic programming.  
In all three cases, we used the Mersenne Twister algorithm to generate random samples \cite{wagner_twister_09}.
